Spit-Apply-Combine with Collapsing Groups

### 2022-10-31 paper/paper.tex
few fixes, ideas, and added csh_from_digits

Let us see how the elements $U$, $f\to A$ and $\phi$ are implemented
in practice. Consider the signature of the R \texttt{aggregate} function for data
frames (we skip arguments that are not important for the discussion).
\begin{verbatim}
  aggregate(x, by, FUN)
\end{verbatim}
Here, \texttt{x} is a data frame where each column is a variable to be
aggregated.  The argument \texttt{by} represents the label(s) for each record
that are to be used for grouping. So the function $f\to A$ is implemented by
forcing the user to make sure that the position of each label in \texttt{by}
corresponds to the row number in the data frame \texttt{x}. The argument
\texttt{FUN} is the function that aggregates each subset of \texttt{x}.  Here is
an example of how a user might use this function on the R prompt.
%
\begin{verbatim}
> aggregate(iris["Sepal.Length"], by=iris["Species"], FUN=mean)
     Species Sepal.Length
1     setosa        5.006
2 versicolor        5.936
3  virginica        6.588
\end{verbatim}
%
Note that the correspondence in position of the \texttt{Species} label and the
record position is implemented by taking them from the same data frame.

@@

>>>>

Let us see how the elements $U$, $f\to A$ and $\phi$ are implemented
in practice. Consider the signature of the R \texttt{aggregate} function for data
frames (we skip arguments that are not important for the discussion).
\begin{verbatim}
  aggregate(x, by, FUN)
\end{verbatim}
Here, \texttt{x} is a data frame where each column is a variable to be
aggregated.  The argument \texttt{by} represents the label(s) for each record
that are to be used for grouping. So the function $f\to A$ is implemented by
forcing the user to make sure that the position of each label in \texttt{by}
corresponds to the row number in the data frame \texttt{x}. The argument
\texttt{FUN} is the function that aggregates each subset of \texttt{x}.  Here is
an example of how a user might call this function from the R prompt.
%
\begin{verbatim}
> aggregate(iris["Sepal.Length"], by=iris["Species"], FUN=mean)
     Species Sepal.Length
1     setosa        5.006
2 versicolor        5.936
3  virginica        6.588
\end{verbatim}
%
Note that the correspondence in position of the \texttt{Species} label and the
record position is implemented by taking them from the same data frame. The output
also reveals in the first column the set $A$: each row corresponds to a unique
value in \texttt{Species} column.

@@

\begin{itemize}
\item{Specification of collapsing sequence with multiple collapsing variables (e.g. first size class, then NACE code)}
\end{itemize}
